Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-27 lloveras_2020.tex
version final?

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in {particular validation} data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere. Solar rotational tomography is currently the sole observational technique {able to provide} a 3D quantitative description of the solar corona at a global scale. Based on {extreme ultraviolet} images {of space} borne instruments, {differential emision measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$. We carry out a study of the corona {through DEMT} reconstructions {and MHD simulations, using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework. {Two target} rotations were selected from the solar minimum between solar cycles (SC) 23 and 24 and {the {end of the} declining} phase of SC 24. The 3D {DEMT} and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D thermodynamic structure of the inner corona as revealed by the DEMT analysis. We {show the} existence of diverse types of temperature structures in the low and mid latitudes of the {streamer belt. We estimate} the heating energy required to keep them {stable, which we argue may} be accounted for by Alfvén waves. {We also show that results of the latest version of the AWSoM model overal} agree with DEMT {reconstructions within a $\approx 20\%$ accuracy. We highlight some details of the AWSoM model that should} be improved to better reproduce {tomographic} results, in particular concerning the source region of the {fast and slow components of the solar wind.}}
\end{abstract}

@@

To study the {3D structure of the quiet-Sun global corona,} SRT has proven to be a powerful tool. {In SRT, solar rotation is taken advantage of, so that instruments gather time series of images covering all viewing angles of the solar corona. This allows posing an inversion problem to solve for the uncknown 3D distribution of specific quantities of the solar corona. Based on extreme ultraviolet EUV images, taken in several channels sensitive to different temperatures, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM). The final product of DEMT is in the form of 3D maps of electron density and temperature, covering the range of heliocentric heights $\lesssim 1.25\,\mrsun$.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. {A recent review on DEMT was published by \citet{vasquez_2016}. The technique is summarized in Section \ref{demt}.}

@@

The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space {Wea\-ther} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}. {The single data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation. As new improvements are implemented, the model is continuously being validated with observations.} DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona. More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.

@@

{Combining the DEMT and AWSoM models, we carry out a detailed quantitatively analysis of two target rotations. We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24. {In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} {(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG). In the case of CR-2208, the DEMT analysis is based in data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} {(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}

@@

{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we {opt} to only use off-limb data. In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included. This has two implications. Fistly, the fast dynamics that typically characterizes those structures is abscent from the data. Sencondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume. As a result, {artifacts induced by coronal dynamics} are reduced compared to previous DEMT reconstructions.}

{The solution of the tomographic problem involves {inversion of} a very large sparse matrix. Such inversion problems are characterized by spurious {high-fre\-quen\-cy} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}. In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude. Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives. In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions. As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid {when compared to previous reconstructions.}}

@@

\begin{equation}\label{fbeldem}
\FBE_i^{(k)}  = \int\,\textrm{d}T\,\LDEM_i(T)\,{\TRF}^{(k)}(T), \ \ \ {k=1,...,K}
\end{equation}

@@

To drive {the AWSoM model, estimates} of the photospheric magnetic field of the Sun {are the main} input. Synoptic magnetograms are used to specify the initial and the boundary conditions of the {magnetic field.} We use the PFSS model to extrapolate the 3D magnetic field (from the 2D photospheric magnetic field maps) using spherical harmonics. The source surface is taken to be at 2.5 $\mrsun$. The Global Oscillation Network Group (GONG) provides synoptic full-disk surface maps of the radial magnetic field component of the Sun. However, since the polar regions are not well observed from the ecliptic, GONG estimates the polar fields by fitting a polynomial to neighboring observed latitudes, which might lead to inaccuracies. An improvement over these maps is provided by the Air Force Data Assimilation Photospheric Flux Transport (ADAPT) model \citep{Wor2000}, which creates synchronic-synoptic maps by incorporating supergranulation, meridional circulation, and differential rotation. These maps provide a physics-based description of the unobserved polar magnetic fields \citep{Arg2010, Hen2012}. In this work, we use the GONG synoptic map as input for CR-2082 (ADAPT-GONG maps are unavailable for CR-2082) and the ADAPT-GONG global magnetic field map for CR-2208. {Based on results from previous efforts, for CR-2082} the magnetic field from the GONG map is scaled up by a factor of 1.85 {for weak fields ($B_r< 5\,\rm{G}$), while no modification is applied in the case of} the ADAPT-GONG map for CR-2208. The AWSoM steady-state simulation set-up and input parameters for both rotations are described below.

To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent {equal to} 0.21 and the amplitude equal to {0.18, for both} rotations. The boundary condition for Alfv\'{e}n wave energy is given by the {poynting flux ($S_{A}$)} of the outgoing {wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, whith $B_{\odot}$ being the field} strength at the inner boundary. The correlation length of the Alfv\'{e}n waves is set {to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$.}

{The computational domain of the solar corona} extends from 1 to {$24\,\mrsun$}. The spherical grid in the solar corona is radially stretched (with a maximum resolution {of $0.001\,\mrsun$} near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates. The Adaptive Mesh Refinement (AMR) resolves the angular cell {size to $1.4\mdeg$ in the range of heights $1-1.7\,\mrsun$ and beyond $2.8\,\mrsun$}. \notebyalbert{(by Albert) does this make sense?} The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082. Local time stepping is used to speed up the steady state convergence. The AWSoM simulation results of the structure of the solar corona for solar minimum conditions represented by CR-2082 and CR-2208 are compared to the DEMT as described in the results section.

\subsection{{Tracing Results Along Magnetic Field lines}}\label{trace}

@@

\begin{eqnarray}\label{Nfit}
\sqravgN &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
\label{Tfit}
\Tm &=& T_0\,+\,m\,h
\end{eqnarray}

@@

\begin{enumerate}
\item 
The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg. {This requirement is set to ensure a reasonably spread sample of heights along the leg.}
\item 
The {DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
\item 
{The condifence level of both the exponential and linear fits must be larger than 90\%.} 
\end{enumerate}

@@

{Legs of type down turn out to have a significant population only for closed-small loops. In the case of closed-large loops and open field lines, there are very few cases of type down. Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}. \\
In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed. {As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}

@@

{The high temperature of the corona requires heating mechanisms to compensate for the energy losses. While the vast majority of the existing literature on coronal heating focuses on active regions (ARs), some studies have been dedicated to the heating of quiet-Sun regions. In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to mantain stability. The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in Section \ref{trace}.}

@@

\noindent
where $s$ is the position along {the flux tube} and the {power quntities} are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.

@@

{The energy balance given by Equation \ref{Balance} is then integrated in the volume of any given coronal magnetic flux tube. Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal conditon of the magnetic field, a {field line integrated} version of that energy balance is found,
\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + \phi_c,
\end{equation}
\noindent
where the {line-integrated} flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017},} \\

@@

\noindent {where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {Note that, for any given field line, all quantities in these two expresions can be computed {from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}. Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to mantain a stable coronal structure.}

@@

{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations. Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of {the} tomographic grid ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}. Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}). Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model\albert{, detailed in Section \ref{awsom}.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2082_fulltriple_gradt.eps}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_fulltriple_gradt.eps}
\caption{Frequency histograms of the temperature radial gradient for {the four types of legs} in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
\label{gradt_demt}
\end{center}
\end{figure}

@@

\albert{Figure \ref{Br} shows carrington maps of {the radial} magnetic {field ($B_r$)} for both rotations at $1.005\, \mrsun$. {Both maps clearly show the large-scale dipolar field, characteristic of solar minimum conditions. Differences between both maps are observed in the sub-polar latitudes, due to the different treatments applied there by the GONG (CR-2082) and the ADAPT-GONG (CR-2208) maps.}}

@@

{{Several details from Figure \ref{perf_lat} are worth being highlighted. Firstly, at most latitudes the overal agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208. The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much. In the case of the electron temperature, for both target rotations the models agree within $\approx 15\%$ at all latitudes of the streamer belt, showing larger discrepancies in the CHs.} Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterising the low-latitudes of the equatorial streamer belt compared to its mid-latitudes. Thirdly, for both target rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density. Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary. Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend. {For comparison, note the beahavior of $B_r$ in the CHs, increasing from the open/closed boudary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}

@@

{For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, {depending of the type of leg, with the largest discrepancy foud for legs of type II (near the open/closed boundary). The} median value of the scale height $\lN$ agree {within $\approx 10\%$ in all regions}. The leg-averaged electron temperature $\aTm$ of both models also agree {within $10\%$ in all regions}. For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models {is within $10\%$, while} median values of $\aTm$ agree within $15\%$. {These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compard to DEMT in different magetic strucures.}}

@@

{As discussed above, Figure \ref{perf_lat} shows that the logitude-averaged latitudinal profile of the DEMT electron density in the CHs decreases towards the poles. Figure \ref{perf_lon_vr} below shows the longitude-averaged AWSoM radial wind speed $V_r$ at $6\,\mrsun$, where all field lines are open. The heliocentric current sheet (HCS) location is indicated by the minimum of the speed curve. For each rotation, all velocity data points to the south of the HCS position map down to the southern CH in Figures \ref{perf_lat}. Similarly, all velocity data points to the north of the HCS position map down to the northern CH in Figures \ref{perf_lat}. This clearly shows an anti-correlation between the DEMT electron density at low heights and the AWSoM wind speed at larger heights.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995_2.pdf}
\caption{{Longitude-averaged latitudinal dependence of the AWSoM model \albert{wind speed $V_r$} at $6.0\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).}}
\label{perf_lon_vr}
\end{center}
\end{figure}

@@

{Based on the magnetic field of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types. \albert{Small loop legs} in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I). \albert{Large closed legs} of type up that form the envelope of the streamer belt (dubbed type II), and open field lines of type up populating the CHs (dubbed type III).}

@@

{{For both target rotations}, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer. In the case of the \albert{DEMT reconstruction based on AIA data we show that, in} a substantial fraction of the \albert{voxels of the CHs,} the technique performs poorly in modeling \albert{an LDEM that predicts} the tomographic emissivitiy in each EUV band with reasonable accuracy. As a result, DEMT results based on AIA data \albert{are less reliable CHs}. This was already found by the existing two previous DEMT works based on AIA data \citep{nuevo_2015,maccormack_2017}. The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets. We are currently implementing an improved LDEM determination algorithm to to deal with this issue that will be used in a follow up article.}

>>>>

\begin{abstract}
Observational techniques play an essential role in advancing our understanding of the physical processes governing the solar corona, providing in {particular validation} data for three-dimensional (3D) magnetohydrodynamic (MHD) models of the solar atmosphere. Solar rotational tomography is currently the sole observational technique {able to provide} a 3D quantitative description of the solar corona at a global scale. Based on {extreme ultraviolet} images {of space} borne instruments, {differential emission measure tomography (DEMT)} allows constructing 3D maps of the coronal electron density and temperature at heliocentric heights below $\approx 1.25\,\mrsun$. We carry out a study of the corona {through DEMT} reconstructions {and MHD simulations, using} the latest version of the Alfv\'en Wave Solar Model (AWSoM) developed at the University of Michigan as a component of the Space Weather Modeling Framework. {Two target} rotations were selected from the solar minimum between solar cycles (SCs) 23 and 24 and {the {end of the} declining} phase of SC 24. The 3D {DEMT} and MHD models are analysed and compared in distinct coronal magnetic structures. {We report in quantitative detail on the 3D thermodynamic structure of the inner corona as revealed by the DEMT analysis. We {show the} existence of diverse types of temperature structures in the low and mid latitudes of the {streamer belt. We estimate} the heating energy required to keep them {stable, which we argue may} be accounted for by Alfvén waves. {We also show that results of the latest version of the AWSoM model overal} agree with DEMT {reconstructions within a $\approx 20\%$ accuracy. We highlight some details of the AWSoM model that should} be improved to better reproduce {tomographic} results, in particular concerning the source region of the {fast and slow components of the solar wind.}}
\end{abstract}

@@

To study the {3D structure of the quiet-Sun global corona,} SRT has proven to be a powerful tool. {In SRT, solar rotation is taken advantage of, so that instruments gather time series of images covering all viewing angles of the solar corona. This allows posing an inversion problem to solve for the unknown 3D distribution of specific quantities of the solar corona. Based on extreme ultraviolet (EUV) images, taken in several channels sensitive to different temperatures, differential emission measure tomography (DEMT) allows reconstruction of the 3D distribution of the differential emission measure (DEM). The final product of DEMT is in the form of 3D maps of electron density and temperature, covering the range of heliocentric heights $\lesssim 1.25\,\mrsun$.} The technique was first developed by \citet{frazin_2009}, and first applied to the observational study of coronal structures by \citet{vasquez_2009}. {A recent review on DEMT was published by \citet{vasquez_2016}. The technique is summarized in Section \ref{demt}.}

@@

The Alfv\'{e}n Wave Solar atmosphere Model (AWSoM) within the Space {Weather} Modeling Framework (SWMF) is a three-dimensional (3D) physics-based, data-driven MHD model extending from the upper chromosphere, to the upper corona and to {1 AU and beyond} \citep{vander_2010, Van2014}. {The single data input of the model is a magnetogram of the global corona, used as boundary condition for the simulation. As new improvements are implemented, the model is continuously being validated with observations.} DEMT results were used by \citet{jin_2012} and \citet{oran_2015} to validate AWSoM results finding an agreement within 50\% in density and electron temperature in the low corona. More recently, \citet{sachdeva_2019} compared the results of the latest version of AWSoM model with DEMT products in a globally fashion, obtaining an agreement within 20\%.

@@

{Combining the DEMT and AWSoM models, we carry out a detailed quantitatively analysis of two target rotations. We selected Carrington rotation} (CR)-2082 (2009, 05 April through 03 May) during the Solar Cycle (SC) 23/24 minimum, and CR-2208 (2018, 02 September through 29 September) during {the end of the declining} phase of SC 24. {In the case of CR-2082, the DEMT analysis is based on data} taken by the \textit{Extreme UltraViolet Imager Behind} {(EUVI-B: \citealt{wuelser_2004})} on board the \textit{Solar TErrestrial RElations Observatory} {(STEREO), while the AWSoM model uses the synoptic magnetogram provided by the Global Oscillation Network Group (GONG: \citealt{gong}). In the case of CR-2208, the DEMT analysis is based in data taken} by the \textit{Atmospheric Imaging Assembly instrument} {(AIA: \citealt{lemen_2012})} on board the \textit{Solar Dynamics Observatory} {(SDO), while the AWSoM model uses the magnetogram provide by the Air Force Data Assimilation Photospheric flux Transport (ADAPT)-GONG model.}

@@

{While in all previous DEMT studies full-disk data was used to perform tomography, in this work we {opt} to only use off-limb data. In this way, the smallest scale and brighter coronal features seen on disk (most typically in the 171\AA\ band) are not included. This has two implications. Firstly, the fast dynamics that typically characterizes those structures is absent from the data. Secondly, only half synodic rotation worth of data is needed to constrain the inversion problem for the whole coronal volume. As a result, {artifacts induced by coronal dynamics} are reduced compared to previous DEMT reconstructions.}

{The solution of the tomographic problem involves {inversion of} a very large sparse matrix. Such inversion problems are characterized by spurious {high-frequency} artifacts in the solution, which can be mitigated through {regularization} techniques \citep{frazin_2000}. In the case of DEMT, all previous efforts used the 2D scheme implemented by \citet{frazin_2009}, using a finite difference matrix operator to approximate angular derivatives in both latitude and longitude. Also new to the present work, is the implementation of an expanded 3D regularization scheme, which adds to the previous scheme a finite difference matrix operator to approximate radial derivatives. In this way, the tomographic inversion problem is performed penalizing nonphysical high-frequency artifacts in all three spatial directions. As a result, tomographic reconstructions behave more smoothly close to the radial boundaries of the computational grid {when compared to previous reconstructions.}}

@@

\begin{equation}\label{fbeldem}
\FBE_i^{(k)}  = \int\,\textrm{d}T\,\LDEM_i(T)\,{\TRF}^{(k)}(T), \ \ \ {k=1,...,K} \,,
\end{equation}

@@

To drive {the AWSoM model, estimates} of the photospheric magnetic field of the Sun {are the main} input. Synoptic magnetograms are used to specify the initial and the boundary conditions of the {magnetic field.} We use the PFSS model to extrapolate the 3D magnetic field (from the 2D photospheric magnetic field maps) using spherical harmonics. The source surface is taken to be at 2.5 $\mrsun$. GONG provides synoptic full-disk surface maps of the radial magnetic field component of the Sun. However, since the polar regions are not well observed from the ecliptic, GONG estimates the polar fields by fitting a polynomial to neighboring observed latitudes, which might lead to inaccuracies. An improvement over these maps is provided by the Air Force Data Assimilation Photospheric Flux Transport (ADAPT) model \citep{Wor2000}, which creates synchronic-synoptic maps by incorporating supergranulation, meridional circulation, and differential rotation. These maps provide a physics-based description of the unobserved polar magnetic fields \citep{Arg2010, Hen2012}. In this work, we use the GONG synoptic map as input for CR-2082 (ADAPT-GONG maps are unavailable for CR-2082) and the ADAPT-GONG global magnetic field map for CR-2208. {Based on results from previous efforts, for CR-2082} the magnetic field from the GONG map is scaled up by a factor of 1.85 {for weak fields ($B_r< 5\,\rm{G}$), while no modification is applied in the case of} the ADAPT-GONG map for CR-2208. The AWSoM steady-state simulation set-up and input parameters for both rotations are described below.

To account for the energy partitioning between electrons and protons, based on \citet{Cha2011}, we set the stochastic heating exponent {equal to} 0.21 and the amplitude equal to {0.18, for both} rotations. The boundary condition for Alfv\'{e}n wave energy is given by the {poynting flux ($S_{A}$)} of the outgoing {wave, $({S_{A}/}{B})_{\odot} = 1.1\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ and $1.0\times 10^{6}$\,W\,m$^{-2}$\,T$^{-1}$ for CR-2082 and CR-2208, respectively, with $B_{\odot}$ being the field} strength at the inner boundary. The correlation length of the Alfv\'{e}n waves is set {to, $L_{\perp} \sqrt{B} = 1.5 \times 10^{5}$m\,$\sqrt{T}$.}

{The computational domain of the solar corona} extends from 1 to {$24\,\mrsun$}. The spherical grid in the solar corona is radially stretched (with a maximum resolution {of $0.001\,\mrsun$} near the Sun) with the z-axis aligned with the rotation axis in Heliographic Rotation coordinates. The Adaptive Mesh refinement (AMR) resolves the angular cell size to $1.4\mdeg$ between $1 - 1.7\,\mrsun$ and to $2.8\mdeg$ outside this radius range. The solar corona component uses about 3 million cells on a $6 \times 8 \times 8$ grid blocks (for CR-2208) and $6 \times 4 \times 4$ grid blocks for CR-2082. Local time stepping is used to speed up the steady state convergence. The AWSoM simulation results of the structure of the solar corona for solar minimum conditions represented by CR-2082 and CR-2208 are compared to the DEMT as described in the results section.

\subsection{{Tracing Results Along Magnetic Field Lines}}\label{trace}

@@

\begin{eqnarray}\label{Nfit}
\sqravgN &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]} \,,\\
\label{Tfit}
\Tm &=& T_0\,+\,m\,h \,,
\end{eqnarray}

@@

\begin{enumerate}
\item 
The leg must go through at least five tomographic grid cells with reconstructed data, and there must be at least one data point in each third of the range of heights spanned by the leg. {This requirement is set to ensure a reasonably spread sample of heights along the leg.}
\item 
The {DEMT temperature and height data points must meet} $|\rhoTr| > 0.5$.
\item 
{The confidence level of both the exponential and linear fits must be larger than 90\%.} 
\end{enumerate}

@@

{Legs of type down turn out to have a significant population only for closed-small loops. In the case of closed-large loops and open field lines, there are very few cases of type down. Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}. \\
In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic structures are statistically analysed. {As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}

@@

{The high temperature of the corona requires heating mechanisms to compensate for the energy losses. While the vast majority of the existing literature on coronal heating focuses on active regions (ARs), some studies have been dedicated to the heating of quiet-Sun regions. In particular,  \citet{maccormack_2017} developed a new application of the DEMT technique to estimate the energy input flux required at the base of quiet-Sun coronal loops to maintain stability. The technique is based on tracing the DEMT results along field lines of a global coronal magnetic model, just as described in Section \ref{trace}.}

@@

\noindent
where $s$ is the position along {the flux tube} and the {power quantities} are in units of $[{\rm erg\,sec^{-1}\,cm^{-3}}]$.

@@

{The energy balance given by Equation \ref{Balance} is then integrated in the volume of any given coronal magnetic flux tube. Dividing the result by the flux tube area at the coronal base, and making use of the soleidonal condition of the magnetic field, a {field line integrated} version of that energy balance is found,
\begin{equation}\label{FluxBalance}
\phi_h = \phi_r + \phi_c,
\end{equation}
\noindent
where the {line-integrated} flux quantities $\phi_{r,c}\,[\rm{erg\,sec^{-1}\,cm^{-2}}]$ are given by \citep{maccormack_2017}:} \\

@@

\noindent {where $L$ is the length of the loop, and $B_0$ and $B_L$ are the values of the magnetic field at the footpoint locations of the loop in the coronal base, namely $s=0$ and $s=L$.} {Note that, for any given field line, all quantities in these two expressions can be computed {from the DEMT results traced along field lines, and the AWSoM magnetic field model,} through Equations \ref{Fc}-\ref{Er}. Once computed, the quantity $\phi_h$ can be calculated, which is the energy input flux required at the coronal base of each coronal field-line to maintain a stable coronal structure.}

@@

{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations. Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of {the} tomographic grid ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}. Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}). Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model{, detailed in Section \ref{awsom}.}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2082_full_doble_errortriple_gradt.eps}
\includegraphics[width=0.495\textwidth,height=0.25\textwidth,clip=]{figs/histo_cr2208_full_doble_errortriple_gradt.eps}
\caption{Frequency histograms of the temperature radial gradient for {the four types of legs} in Figure \ref{rpoint_demt} (using the same color code) for CR-2082 (left panel) and CR-2208 (right panel).}
\label{gradt_demt}
\end{center}
\end{figure}

@@

{Figure \ref{Br} shows carrington maps of {the radial} magnetic {field ($B_r$)} for both rotations at $1.005\, \mrsun$. {Both maps clearly show the large-scale dipolar field, characteristic of solar minimum conditions. Differences between both maps are observed in the sub-polar latitudes, due to the different treatments applied there by the GONG (CR-2082) and the ADAPT-GONG (CR-2208) maps.}}

@@

{{Several details from Figure \ref{perf_lat} are worth being highlighted. Firstly, at most latitudes the overall agreement of the electron density of both models is within $\approx 20\%$ for CR-2082, and $\approx 5\%$ for CR-2208. The noticeable exception is to be found near the open/closed boundaries of both target rotations, where the disagreement between both models can be up to twice as much. In the case of the electron temperature, for both target rotations the models agree within $\approx 15\%$ at all latitudes of the streamer belt, showing larger discrepancies in the CHs.} Secondly, for both target rotations, and for both models, these plots clearly show the relatively lower temperatures characterizing the low-latitudes of the equatorial streamer belt compared to its mid-latitudes. Thirdly, for both target rotations, the latitude of the open/closed magnetic boundary in both hemispheres matches the location of the strongest latitudinal gradient of the DEMT electron density. Note this is not the case for the AWSoM model, that shows a minimum density at the open/closed boundary. Last, note that the DEMT electron density decreases from the open/closed boundary towards the poles (in both hemispheres of the two target rotations), while the AWSoM model shows the opposite trend. {For comparison, note the behavior of $B_r$ in the CHs, increasing from the open/closed boundary towards the poles for CR-2082, while showing local maxima around latitudes $-75\mdeg$ and $+70\mdeg$ in the case of CR-2208.}}

@@

{For target rotation CR-2082, the median value of the electron density $\NCB$ of both models agree within $\approx 10-25\%$, {depending of the type of leg, with the largest discrepancy foud for legs of type II (near the open/closed boundary). The} median value of the scale height $\lN$ agree {within $\approx 10\%$ in all regions}. The leg-averaged electron temperature $\aTm$ of both models also agree {within $10\%$ in all regions}. For target rotation CR-2208 the agreement of the median value of $\NCB$ and $\lN$ of both models {is within $10\%$, while} median values of $\aTm$ agree within $15\%$. {These detailed results, being consistent with the large-scale comparison provided in Figure \ref{perf_lat}, show in detail how the AWSoM model performs compared to DEMT in different magnetic structures.}}

@@

{As discussed above, Figure \ref{perf_lat} shows that the longitude-averaged latitudinal profile of the DEMT electron density in the CHs decreases towards the poles. Figure \ref{perf_lon_vr} below shows the longitude-averaged AWSoM radial wind speed $V_r$ at $6\,\mrsun$, where all field lines are open. The heliocentric current sheet (HCS) location is indicated by the minimum of the speed curve. For each rotation, all velocity data points to the south of the HCS position map down to the southern CH in Figures \ref{perf_lat}. Similarly, all velocity data points to the north of the HCS position map down to the northern CH in Figures \ref{perf_lat}. This clearly shows an anti-correlation between the DEMT electron density at low heights and the AWSoM wind speed at larger heights.}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2082_5995_2.pdf}
\includegraphics[width=0.495\textwidth]{figs/Perfil_Vr_2208_5995_2.pdf}
\caption{{Longitude-averaged latitudinal dependence of the AWSoM model {wind speed $V_r$} at $6.0\,\mrsun$ for CR-2082 (left panel) and CR-2208 (right panel).}}
\label{perf_lon_vr}
\end{center}
\end{figure}

@@

{Based on the magnetic field of AWSoM model and the results of the DEMT model for electron density and temperature, we classified coronal structures in four different types. {Small loop legs} in the core of the streamer belt are classified in down/up types according to their temperature decreasing/increasing with height (dubbed type 0/I). {Large closed legs} of type up that form the envelope of the streamer belt (dubbed type II), and open field lines of type up populating the CHs (dubbed type III).}

@@

{{For both target rotations}, type III field lines in the CHs are characterized by sub-MK temperatures, and electron density values of order $\approx 1/2$ of those observed for the type 0 and type I lines in the core of the equatorial streamer. In the case of the {DEMT reconstruction based on AIA data we show that, in} a substantial fraction of the {voxels of the CHs,} the technique performs poorly in modeling {an LDEM that predicts} the tomographic emissivity in each EUV band with reasonable accuracy. As a result, DEMT results based on AIA data {are less reliable CHs}. This was already found by the existing two previous DEMT works based on AIA data \citep{nuevo_2015,maccormack_2017}. The source of this distinct performance of DEMT when applied to EUVI or AIA data is related to the TRFs of the respective filter sets. We are currently implementing an improved LDEM determination algorithm to to deal with this issue that will be used in a follow up article.}
